Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-12 longoutput.tex
Change notation

We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H=H\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

>>>>

We consider the transform $\mathcal{F}(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H=H\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.
